DOM bridges and barriers: systematic review and survey

### 2025-09-28 reports/draft_results.qmd
assemble radar and stack

@@

#stacked bar plots
stack_survey <- ggplot(freq_job_survey2, aes(fill=code_level, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "Sub-theme") +
    theme_ms() +
    xlab("") + 
    ylab("Proportion of theme (%)")

@@

top_survey <- freq_job_survey3 %>% group_by(fish_ship, bridge_barr) %>% arrange(desc(value)) %>% top_n(3) %>% ungroup()

top_bridge <- top_survey %>% 
  filter(bridge_barr == "Bridge") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

top_barrier <- top_survey %>% 
  filter(bridge_barr == "Barrier") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

radar_br_survey <- ggradar::ggradar(top_bridge,
        values.radar = c(0, 14, 22), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3.5)

radar_ba_survey <- ggradar::ggradar(top_barrier,
        values.radar = c(0, 17, 28), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3.5)

stack_survey | radar_br_survey | radar_ba_survey
```

>>>>

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 7
#| fig-align: center
#| include: false

@@

#stacked bar plots
ggplot(freq_job_survey2, aes(fill=code_level, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "Sub-theme") +
    theme_ms() +
    theme(legend.position = "right")+
    xlab("") + 
    ylab("Proportion of theme (%)")

#ggsave("figures/ms_figs/industry/stack_survey.png", width = 7, height = 6, units = c("in"))

@@

top_survey <- freq_job_survey3 %>% 
                group_by(fish_ship, bridge_barr) %>% 
                arrange(desc(value)) %>% 
                top_n(3) %>% 
                ungroup() %>%
                select(code_name)

top_bridge <- freq_job_survey3 %>%
  subset(code_name %in% top_survey$code_name) %>% 
  filter(bridge_barr == "Bridge") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

top_barrier <- freq_job_survey3 %>%
  subset(code_name %in% top_survey$code_name) %>%
  filter(bridge_barr == "Barrier") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

ggradar::ggradar(top_bridge,
        values.radar = c(0, 16, 22), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

#ggsave("figures/ms_figs/industry/radar_br_survey.png", height = 8, width = 8, units = c("in"))

ggradar::ggradar(top_barrier,
        values.radar = c(0, 17, 28), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

#ggsave("figures/ms_figs/industry/radar_ba_survey.png", height = 8, width = 8, units = c("in"))

::: panel-tabset

#### Surveys

![](images/survey_combo.png){fig-align="center" width="5in", height = "8in"}

#### Literature

:::
